Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-19 Grassmannian_cells.tex
continued improving section 5

\subsection{Fibrations of Quiver Grassmannians}

@@

\end{definition}
We introduce a notion of equivalence of $2$-quivers.
\begin{definition}\label{def:2equivalence}
Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that $\Gamma(1)$ has precisely one source $q$ and $\Gamma(2)$ has precisely one sink $q'$. Let $\tilde Q_V$ be the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:q\to q'$. This defines a relation on the set of $2$-quivers denoted by $\tilde Q_V\to \tilde Q$. Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation. 
\end{definition}
Observe that the set of vertices of two equivalent $2$-quivers coincide.
\begin{lemma}
Let $\tilde Q$ and $\tilde Q'$ be two equivalent $2$-quivers. If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
The number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
\end{lemma}
\begin{proof}
We may assume that $\tilde Q'=\tilde Q_V$ where $V:\Gamma(1)\to\Gamma(2)\in Q_2$. As in Definition \ref{def:2equivalence}, we denote the unique source of $\Gamma(1)$ by $q$, the unique sink of $\Gamma(2)$ by $q'$ and the new arrow by $\alpha_V:q\to q'$.

@@

The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians. Therefore, we use the recursive construction described in Section \ref{Lifting}. In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering. Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$.

Actually, all $2$-quivers can be built from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$, where we define $P_2^{(n-1)}$ by the lift (using the conventions of Example \ref{smallm}):
\[
  \tilde P_2^{(n-1)}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
\]

%In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
%\[
%  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}.
%\]
Choosing the lifts of $P_1$ supported at $(1,\alpha_2),\ldots,(1,\alpha_n)$, we have 
\[
  \Ext(P_2^{(n-1)},P_1)\cong\langle (2,1)\xrightarrow{\alpha_l}(1,\alpha_l)\mid l=2,\ldots,n\rangle.
\]

This defines recursively the truncated preprojective representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ by the lifts 
\begin{align}
  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
\end{align}
Note that we have a short exact sequence
\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
We define the $2$-quiver of $P_2^{(k)}$ by
\\

\begin{tikzpicture}
\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

@@

The next step is to define the $2$-quivers of certain truncated preprojectives $P^{(k)}_3$ whence the remaining $2$-quivers attached to truncated preprojectives $P_m^{(k)}$ can be obtained recursively. In view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any truncated preprojective of this dimension.

As in Section \ref{Lifting}, let $\tilde P_2$ be supported at $(2,1)$. Then we have 
$$\Ext(P_2^{(1)},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_2^{(1)},\alpha_i^{-1}\alpha_n\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_2^{(1)},P_2)$, each basis element given by the linear map $$(2,1)\xlongrightarrow{\alpha_n}(1,\alpha_n)\in\Hom_{\CC}((\tilde P_2^{(1)})_{(2,1)}),(\alpha_i^{-1}\alpha_n\tilde P_2)_{(1,\alpha_n)})$$
for $i=1,\ldots,n-1$.

Now define $\tilde P_3^{(n-1)}:=\tilde P_2^{(1)}$

This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation. Note that the middle vertex of $P_3^{(n-1)}$ is $(2,1)$ and that all $2$-arrows end in a vertex corresponding to the vertex $(1,\alpha_n)$ of $\widetilde{K(n)}$.\\

@@

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{(1)}$} ; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$P_3^{(2)}$};

\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{(n-3)}$} ; 
\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-2}$};
\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{(n-2)}$}; 
\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{(n-1)}$}   ; 
\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $\alpha_2$};
\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $\alpha_{n-1}$};
%\tikzstyle{every node}=[circle,fill=white!10]
\node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
%\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$\alpha_{n}$};
\node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$\alpha_{n}$};
\node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$\alpha_{n}$};
\node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};

\node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$\alpha_{n}$};
\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$\alpha_{n}$};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$\alpha_{n}$};

@@

We have $\dim \Hom(P_{m-1},\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_{m-1})=n-k$. If a basis of $\Ext(P_m^{(k)},P_{m-1})$ is compatible with a lift to the universal covering,  there is a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{(k)})$. For $m=3$, the lift of $\tau P_3^{(k)}$ is given by 
\[\xymatrix@R10pt@C20pt{&&(2,\alpha_1^{-1})\ar_{\alpha_1}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_k^{-1})\ar_{\alpha_{k}}[llu]}.\]
The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{\alpha_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{\alpha_l} i_l$. Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{(k)}$ to the image of the corresponding homomorphism $P_2\to P_1^{(k)}$ which is of dimension $(1,1)$. In the above illustration, we forgo to insert the corresponding rectangles and just connected the $2$-arrows to the sinks of the corresponding subquivers. It can be seen that this is no restriction from the combinatorial point of view.

We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$. If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, it is straightforward to get a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$.
Now we can recursively the $2$-quivers of $P_m^{(k)}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating this procedure. For $m\geq 4$, the truncated preprojective $\tau P_m^{(k)}$ can uniquely be found as a quotient of $P_m$.
Recall that we have $\udim P_m^{(k)}=\udim P_{m-1}^{(1)}+(n-k-1)\udim P_{m-1}$. Moreover, we have 
\[\dim \Hom(P_{m-1},\tau P_m^{(1)})=\dim\Ext(P_m^{(1)},P_{m-1})=n-1.\]

As before we get a one-to-one correspondence between basis elements when passing to the universal covering quiver. More precisely, we can take the BGP-reflected basis of the basis of $\Ext(P_2^{(1)},P_2)$ from above.

Let us assume that we already constructed the $2$-quiver of $P_{m+1}^{(k)}$. The $2$-quiver of $P^{(k-1)}_{m+1}$ is given by glueing the $2$-quiver of $P_{m+1}^{(k)}$ to the one of $P_{m}$
\\

\begin{tikzpicture}
\draw (0,4) node (A1) {$P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$P_{m}$} +(1.5,0) node (B1) {$P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$P_{m}^{(1)}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$P_{m-1}$}  +(6,0) node (E1) {$P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$P_{m}^{(n-2)}$}+(6,-.9) node (P51) {\footnotesize$P_{m-1}^{(1)}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$P_{m-1}^{(k)}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$P_{m-1}^{(n-2)}$} +(13.5,0) node (E1b) {$P^{(n-1)}_{m-2}$} ; 
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {};
\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {};
\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {};
\draw[->,red] (Q41)--(E1) node[pos=.5,above] {};
\draw[->,red] (Q51)--(D1) node[pos=.5,above] {};
\draw[->,red] (Q61)--(B11) node[pos=.5,above] {};
\draw[->,red] (Q71)--(B1) node[pos=.5,above] {};
\draw[->,red] (Q81)--(A1) node[pos=.5,above] {};

\draw (0,0) node (B) {$P_{m}$}+(0,-.8) node (P1) {\footnotesize$P_{m+1}^{(k)}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$P_{m}$} +(5,-.7) node (P3) {\footnotesize$P_{m+1}^{(n-2)}$}+(7.5,0) node (D) {$P_{m}$}  +(10,0) node (E) {$P_{m+1}^{(n-1)}=P_{m}^{(1)}$} +(7.5,-.6) node (P4) {\footnotesize$P_{m+1}^{(n-1)}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

>>>>

\subsection{Fibrations of Quiver Grassmannians}\label{sec:fibrations}

@@

\end{definition}
We introduce a notion of equivalence of $2$-quivers.
\begin{definition}\label{def:2equivalence}
Let $\tilde Q=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ such that $\Gamma(1)$ has precisely one source $q$ and $\Gamma(2)$ has precisely one sink $q'$. Let $\tilde Q_V$ be the $2$-quiver obtained from $\tilde Q$ when replacing $V$ by a usual arrow $\alpha_V:q\to q'$. This defines a relation on the set of $2$-quivers denoted by $\tilde Q_V\to \tilde Q$. Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation. 
\end{definition}
Observe that the set of vertices of two equivalent $2$-quivers coincide.
\begin{lemma}\label{lem:2equivalence}
Let $\tilde Q$ and $\tilde Q'$ be two equivalent $2$-quivers. If $\beta\subset Q_0$ is strong successor closed, it also defines a strong successor closed subset of $Q_0'$.
The number of strong successor closed subsets of $Q_0$ coincides with the one of $ Q_0'$.
\end{lemma}
\begin{proof}
We may assume that $\tilde Q'=\tilde Q_V$ where $V:\Gamma(1)\to\Gamma(2)\in Q_2$. As in Definition \ref{def:2equivalence}, we denote the unique source of $\Gamma(1)$ by $q$, the unique sink of $\Gamma(2)$ by $q'$ and the new arrow by $\alpha_V:q\to q'$.

@@

The next step is to associate a $2$-quiver with certain (truncated) preprojective representation $ P_m^{\uj}=F_{K(n)}\tilde P_m^{\uj}$ for $\uj\in I_{n-1}$ whose strong successor closed subsets correspond to the cells of quiver Grassmannians. Therefore, we use the recursive construction described in Section \ref{Lifting}. In particular, we choose bases of the $\Ext$-groups which are compatible with the lifts to the universal covering. Recall that quiver Grassmannians $\Gr_{\tbfe}(P_m^V)$ attached to truncated preprojective representations only depend on $\tbfe$ and $\udim P_m^V$. In particular, in view of Theorem \ref{thm:truncpp}, these $2$-quivers can be seen as being attached to any (truncated) preprojective of this dimension.\sayT{Introduce notation for $2$-quivers associated with $P_m^V$?}.

For simplicity and in order to be in shape(?) with Sections \ref{Lifting} and \ref{sec:fibrations}, we work on the universal cover.
It turns out that all $2$-quivers can be built from the $2$-quivers of the lifts $\tilde P_1$, $\tilde P_2$ and $\tilde P_2^{[n-1]}=\tilde P_2^{(1,\ldots,n-1)}$ as defined in Section \ref{Lifting}, i.e. we have:
\[
  \tilde P_2^{[n-1]}=(1,\alpha_1)\xlongleftarrow{\alpha_1}(2,1).%=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1
\]
We define $P_m^{[k]}:=F_{K(n)}\tilde P_m^{[k]}$.
%In other words, $P_2^{(n-1)}$ is chosen as be the cokernel of a short exact sequence
%\[
%  \ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}.
%\]
Choosing the lifts of $P_1$ supported at $(1,\alpha_2),\ldots,(1,\alpha_n)$, we have 
\begin{align}\label{eq:case2}
  \Ext( P_2^{[n-1]},P_1)\cong \bigoplus_{i=2}^{n}\Ext(\tilde P_2^{[n-1]},\alpha_i\tilde P_{1})\cong\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=2,\ldots,n\rangle.
\end{align}

This defines recursively the truncated preprojective representation $\tilde P_{2}^{[k]}$ for $k=n-1,\ldots,0$ with $\tilde P_2^{[0]}=\tilde P_2$ by 
\begin{align}
  \label{coeff}\xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\ (2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n-k}}[rrd] &&\vdots\\&&(1,\alpha_{n-k})}.
\end{align}
Note that, for general $m\geq 2$, we have a short exact sequence
\[\ses{\Hom(P_{m-1},P_{m-1})}{\Ext(P_m^{[k]},P_{m-1})}{\Ext(P_m^{[k+1]},P_{m-1})}.\]
Thus a basis of $\Ext(P_m^{[k]},P_{m-1})$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext(P_m^{[n-1]},P_{m-1})$.
We define the $2$-quiver of $P_m^{[k]}$ by
\\

\begin{tikzpicture}
\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
\draw (0,0) node (A) {$(1,\alpha_{n-k})$} +(3,0) node (B) {$(1,\alpha_{n-k+1})$}+(3,-.8) node (P1) {\footnotesize$P_2^{[k+1]}$} +(6,0) node (B1) {$\dots$} +(9,0) node (C) {$(1,\alpha_{2})$} +(9,-.7) node (P3) {\footnotesize$P_2^{[n-2]}$}+(11.5,0) node (D) {$(1,\alpha_1)$}  +(14,0) node (E) {$(2,1)$} +(11.5,-.6) node (P4) {\footnotesize$P_2^{[n-1]}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

@@

The next step is to define the $2$-quivers of certain truncated preprojectives $\tilde P^{[k]}_3$ and $P^{[k]}_3$ whence the remaining $2$-quivers attached to truncated preprojectives $P_m^{[k]}$ can be obtained recursively.

Define $\tilde P_3^{[n-1]}:=\tilde P_3^{(1,\ldots,n-1)}=\alpha_n^{-1}\tilde P_2^{[1]}$. We have 
$$\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).$$
This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map $$(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,1)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,1)})$$
for $i=1,\ldots,n-1$.

 This basis recursively gives rise to the following $2$-quiver of $\tilde P_3^{[k]}=\tilde P_3^{(1,\ldots,k)}$ (resp. for $P_3^{[k]}$) for $k=n-1,\ldots,0$ where we drop the indices of the vertices in abuse of notation. Note that the middle vertex of $\tilde P_3^{[n-1]}$ is $(1,1)$ and that all $2$-arrows end in this vertex of $\widetilde{K(n)}$.\\

@@

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{[1]}$} ; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$P_3^{[2]}$};

\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{[n-3]}$} ; 
\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-2}$};
\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{[n-2]}$}; 
\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{[n-1]}$}   ; 
\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $\alpha_1$};
\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $\alpha_2$};
\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $\alpha_{n-1}$};
%\tikzstyle{every node}=[circle,fill=white!10]
\node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
%\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{\scriptsize$\alpha_{n}$};
\node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
\node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {\scriptsize$\alpha_{n}$};
\node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};

\node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {\scriptsize$\alpha_{n}$};
\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {\scriptsize$\alpha_{n}$};

@@

For odd $m$, we have

$$ \Hom(P_{m-1},\tau P_m^{[k]})\cong\bigoplus_{i=k+1}^n\Hom(\alpha_{i}^{-1}\tilde P_{m-1},\tau\tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^n\Ext(\tilde P_m^{[k]},\alpha_i^{-1}\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1})$$.

This means that we can choose a basis of $\Ext(P_m^{[k]},P_{m-1})$ which is compatible with a lift to the universal covering which gives a one-to-one correspondence between basis elements of $\Ext(P_m^{[k]},P_{m-1})$ and $\Hom(P_{m-1},\tau P_m^{[k]})$. The representation $\tau\tilde P_3^{[k]}$ is given by 
\[\xymatrix@R10pt@C20pt{&&(2,\alpha_{k+1}^{-1})\ar_{\alpha_{k+1}}[lld]\\ (1,1) &&\vdots\\&&(2,\alpha_n^{-1})\ar_{\alpha_{n}}[llu]}.\]
Note that the image of the homomorphism of the corresponding exact sequence induced by the respective basis elements is the subquiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,1)$ for $i=k+1,\ldots, n$. Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{[k]}$ to the image of the corresponding homomorphism $\tilde P_2\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$. In view of Lemma \ref{lem:2equivalence}, we forgo to insert the corresponding rectangles around the subquiver and just connected the $2$-arrows to the sinks of the corresponding subquivers. 
It remains to consider the case when $m$ is even. Lemma \ref{AR} yields

\begin{align}\label{eq:case2}
 \Hom(P_{m-1},\tau \tilde P_{m}^{[k]})\cong\bigoplus_{i=k+1}^{n}\Hom(\alpha_i\tilde P_{m-1},\tau \tilde P_{m}^{[k]})\cong \bigoplus_{i=k+1}^{n}\Ext(\tilde P_m^{[k]},\alpha_i\tilde P_{m-1})\cong\Ext(P_m^{[k]},P_{m-1}).
\end{align}

Now we can recursively the $2$-quivers of $P_m^{[k]}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating the procedure. For $m\geq 4$, the truncated preprojective $\tau\tilde P_m^{[k]}$ can uniquely be found as a quotient of $\tilde P_m$.
%Recall that we have $\udim P_m^{[k]}=\udim P_{m-1}^{[1]}+(n-k-1)\udim P_{m-1}$. 
As we have a one-to-one correspondence between basis elements of $\Hom(P_{m-1},\tau P_m^{[1]})$ and $\Ext(P_m^{[1]},P_{m-1})$ when passing to the universal covering quiver, we can proceed as before. Let us assume that we already constructed the $2$-quiver of $P_{m+1}^{[k]}$. The $2$-quiver of $P^{[k-1]}_{m+1}$ is given by glueing the $2$-quiver of $P_{m+1}^{[k]}$ to the one of $P_{m}$
\\

\begin{tikzpicture}
\draw (0,4) node (A1) {$P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$P_{m}$} +(1.5,0) node (B1) {$P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$P_{m}^{[1]}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$P_{m-1}$}  +(6,0) node (E1) {$P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$P_{m}^{[n-2]}$}+(6,-.9) node (P51) {\footnotesize$P_{m-1}^{[1]}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$P_{m-1}^{[k]}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$P_{m-1}^{[n-2]}$} +(13.5,0) node (E1b) {$P^{]n-1]}_{m-2}$} ; 
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {};
\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {};
\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {};
\draw[->,red] (Q41)--(E1) node[pos=.5,above] {};
\draw[->,red] (Q51)--(D1) node[pos=.5,above] {};
\draw[->,red] (Q61)--(B11) node[pos=.5,above] {};
\draw[->,red] (Q71)--(B1) node[pos=.5,above] {};
\draw[->,red] (Q81)--(A1) node[pos=.5,above] {};
